Robustly decorrelating errors with mixed quantum gates

### 2019-05-21 decorrelation/mixed_unitaries.tex
Updates to text before IIIA

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

%-------------Header begins here----------------------------------------
\begin{document}
\title{Advantages of mixed quantum gates for information processing}

@@

\author{Kevin C. Young}
\affiliation{Sandia National Laboratories, Livermore, CA}

@@

\begin{abstract}
Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings and Campbell have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error. Our results extend those of Hastings and Campbell to include robustness to drifting external control parameters. We implement these constructions using a superconducting qubit and will discuss randomized benchmarking results consistent with a marked reduction in coherent error.
\end{abstract}

@@

% ==============================================================================
% Section: Introduction
% ==============================================================================
\section{Introduction}
\label{sec:introduction}
\note{discuss variance narrowing and cite Biercuk}
The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. A critical limiting factor, of course, is errors in the quantum gate operations.

The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or imperfect gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit. They are are  computationally expensive to model and it can be difficult to place tight analytic bounds on circuit performance [cite]. Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment. Systems with stochastic errors can usually be modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.

% \note{don't define diamond norm here}

Quantitative bounds on the performance of a quantum circuit composed of faulty gates can be constructed using the diamond distance, $||\cdot||_\diamond$. This particular metric, defined in Section \ref{sec:representing_quantum_gates}, has the appealing property of being subadditive, namely for a channels $\mathcal{F}_1$, $\mathcal{F}_2$ we have:
\begin{equation}
||\mathcal{F}_1\circ\mathcal{F}_2||_\diamond \leq ||\mathcal{F}_1||_\diamond + ||\mathcal{F}_2||_\diamond
\end{equation}
The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict. Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs. Recent work by Campbell and Hastings\cite{Campbell2017, 1612.01011, 1811.08017}, however, has shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. In this case, the resulting effective quantum process has a diamond distance that grows only quadratically in the over/under rotation angle of the component gates.

\note{Discuss randomized compiling}

@@

@@

In this article we discuss various applications of these mixed unitary controls, and show that the advantages of this approach can be made robust to drift in the gate implementations. We demonstrate that, depending on the objective, different numerical optimizations may be preferred. We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing. Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error. We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.

\note{Discuss the advantages of convex/quadratic programs. Discuss randomized compiling.}

@@

\subsection{Representing Errors in Quantum Gates}
\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device. Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.  But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended. If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the actual gate dynamics action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$. This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.

CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix. A key feature of process matrices is that they act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}, and error maps take an especially nice form in this basis:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as could arise from amplitude damping []. If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate.\footnote{If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$). For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.}

In what follows it will be useful to define the \emph{error generator}, $\mathcal{L}$, associated with a faulty gate: 
\begin{align}
	\label{eq:generator}
	\mathcal{E} 
		&= \exp\left(\mathcal{L}\right) \approx \mathcal{I}_d + \mathcal{L}.
\end{align}
If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms.

\subsection{Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from a situation in which we always apply the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i,
\end{align}
which we call a \emph{mixed quantum gate} or MQG. Error metrics can then be computed in terms of the effective error map, 
\begin{equation}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
\begin{align}
	\label{eq:def_agi}
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d}\\
	\label{eq:def_diamond}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated process matrix, $\mathcal{E}$. If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity [Wallman - Error rates in quantum circuits]. The diamond distance is subaddative [Watroos TQI book] under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the diamond distance of a circuit is less than or equal to the sum of the diamond distances for the component gates.

Because $\epsilon_{\mathcal{F}}$ is linear in the error map, we have:
\begin{equation}
	\epsilon_{\mathcal{F}}\!\left(\mathsf{E}_{\rm eff}\right) = \sum_i w_i \,\epsilon_{\mathcal{F}}(\mathsf{E}_i).
\end{equation}
So there can be little hope of reducing the AGI by combining various implementations. However, the diamond distance is a nonlinear function of error map. As we show in the appendix (\ref{sub:diamond_distance_inequality}):
\begin{equation}
	\label{eq:diamond_ineq}
	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
\end{equation}
So by mixing various implementations, each with a different error channel, the resulting channel can have a diamond distance error less than any of the component implementations.

% One may ultimately be interested in constructing bounds on quantum circuit performance, but which metric will provide the best proxy for that will depend strongly on the circuit in question. the diamond distance is approximately linear in the over-rotation angle of a quantum operation, while the average gate infidelity (AGI), given by 1-$\mathcal{F}$, is generally quadratic in the over-rotation angle of a quantum operation.

% These two metrics also vary significantly in performance on mixed processes.

% From this definition, we can use linearity to compute the AGI of an MQC. We see that the AGI of any MQC will be the convex sum of the constituent fidelities, with the same weighting. The diamond norm, however, is non-linear function of the channel, and can in general be smaller for an MQC than any of the processes being mixed.

% A \textit{mixed quantum gate} (MQC) consists of a set of unitary channels, $\actual_j$, and associated weights, $\sum_j \omega_j = 1$.  The process matrix for a mixed unitary channel is then the weighted sum of the component channels, $\actual_{\rm M} = \sum_j \omega_j \actual_j$, and the associated error channel is simply the weighted sum of the associated error channels, $\error_{\rm M} = \sum_j \omega_j \error_j$.

% When performing a quantum gate, there are often many possible ways of it might be implemented. Campbell and Hastings, for instance, consider gates compiled using the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible.\cite{Campbell2017, 1612.01011} Following this, Campbell considered the important problem of minimizing the diamond norm of the resulting error channel. Given a collection of component channels with error at most $\epsilon$, he showed that Hamiltonians form a convex set containing the origin, then the diamond norm can be quadratically supressed. The diamond norm is a particularly appealing target because the it provides useful error bounds on quantum circuits. However, it is not the only optimization target that can be chosen.

\subsection{A simple example}
\label{sec:simple_example}
\noindent As a simple example, consider a single-qubit and four different implementations of a $\mathsf{PHASE}$ gate: $\{3\pi,\pi,-\pi,3\pi\}$ rotations about the $\sigma_z$-axis. If the control amplitude is too high, then the error maps associated with these four implementations are themselves unitary rotations about the $\sigma_z$-axis with rotation angles $\{3\eta, \eta, -\eta, -3\eta\}$, repectively (and $\eta \ll \pi$).

In such a scenario, if the ultimate goal is to produce a channel whose effect can be Monte Carlo simulated, then a useful approach would be to construct a channel whose errors are Pauli stochastic. Such a channel could be constructed, for instance, by drawing from this collection uniformly at random. More generally, given a collection of control, such a channel could be produced by minimizing the off-diagonal elements of $R$ in Equation \ref{eq:process_matrix}. We implemented such a routine on a superconducting qubit.

The error operator corresponding to a rotation error by angle $\eta$ is then:
\begin{equation}
\error(\eta) =
	\left(\begin{array}{ccccc}
		1 & 0 & 0 & 0 \\ 
		0 & \cos\eta & \sin\eta  & 0  \\
		0 & -\sin\eta & \cos\eta & 0  \\
		0 & 0 & 0 & 1
	\end{array} 	
	\right)
\end{equation}

>>>>

\documentclass[aps,nofootinbib,pra,notitlepage,twocolumn]{revtex4-1}
\usepackage{amsfonts,amsmath,amssymb,amsthm}
 \usepackage{array,bm,color}
\usepackage{epsfig,graphicx,nomencl,revsymb4-1,upgreek,url}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{calc}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\graphicspath{{./figures/}}
\hypersetup{colorlinks=true, pdfauthor=Anthony M. Polloreno, pdftitle=Advantages of mixed quantum gates for information processing, citecolor=blue, linkcolor=blue}
\newcommand{\tr}{{\rm Tr\thinspace}}
\newcommand{\bra}[1]{\ensuremath{\left\langle{#1}\right\vert}}
\newcommand{\ket}[1]{\ensuremath{\left\vert{#1}\right\rangle}}
\newcommand{\braket}[2]{\left\langle #1 | #2 \right\rangle}
\newcommand{\ketbra}[2]{\left| #1 \right\rangle\!\!\!\,\left\langle #2 \right|}
\newcommand{\abs}[1]{\left\vert #1 \right\vert}
\newcommand{\expect}[1]{\ensuremath{\left\langle{#1}\right\rangle}}
\newcommand{\timeorder}{\ensuremath{\underset{\leftarrow}{\mathcal{T}}}}
\newcommand{\ident}{{\mathbb1}}
\newcommand{\order}[1]{\mathcal{O}\left( #1 \right)}
\newcommand{\diag}[1]{\mathrm{diag}\{#1\}}
\newcommand{\trans}[1]{#1^\mathsf{T}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\erf}[1]{Eq.~(\ref{#1})}
\newcommand{\needcite}{{\color{blue}\textsuperscript{[citation needed]}}}
\newcommand{\note}[1]{{\color{red}[#1]}}
\newcommand{\kcy}[1]{{\color{red}[#1]_{\rm{KCY}}}}
\newcommand{\amp}[1]{{\color{red}[#1]_{\rm{AMP}}}}
\newcommand{\deriv}[0]{{\frac{d}{d\vec{\delta}}}}

@@

%-------------Header begins here----------------------------------------
\begin{document}
\title{Robustly decorrelating errors with mixed quantum gates}

@@

\author{Kevin C. Young}
\affiliation{Quantum Performance Laboratory, Sandia National Laboratories, Livermore, CA}

@@

\begin{abstract}
\noindent Coherent errors in quantum operations are ubiquitous. Whether arising from spurious environmental couplings or errors in control fields, such errors can accumulate rapidly and degrade the performance of a quantum circuit significantly more than an average gate fidelity may indicate. As Hastings \cite{Hastings2017} and Campbell \cite{Campbell2017} have recently shown, randomly sampling an ensemble of implementations of a target gate yields an effective quantum channel that well-approximates the target, but with dramatically suppressed coherent error. Our work begins by reformulating the results of Hastings and Campbell as a quantum optimal control problem. We then discuss a family of convex programs designed to improve the performance, implementability, and robustness of the resulting mixed quantum gates. Finally, we implement these mixed quantum gate on a superconducting qubit and discuss randomized benchmarking results consistent with a marked reduction in the coherent error.\\
{[1]} M. B. Hastings, \emph{Quantum Information \& Computation} 17, 488 (2017). \\
{[2]} E. Campbell, \emph{Physical Review A} 95, 042306 (2017).
\end{abstract}

@@

% ==============================================================================
% Section: Introduction
% ==============================================================================
\section{Introduction}
\label{sec:introduction}
\noindent The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016, 1901.08035}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances are promising steps forward on the path towards a computationally useful QIP, the quantum supremacy \cite{1203.5813} milestone has yet to be definitively reached. A critical limiting factor, of course, is errors in the quantum gate operations. \note{I think we can just strike this whole paragraph. I hate these introductions.}

The ultimate impact of a gate error on a quantum circuit depends strongly on both the magnitude and the nature of the error. Systematic, or \emph{coherent}, errors can arise from poorly calibrated controls or approximate gate compilations that induce repeatable, undesired unitary errors on the state of a QIP. Errors of this type are correlated in time may add up constructively or destructively, depending on the circuit. They are are  computationally expensive to model and, because coherent errors may amplify when gates are repeated, it can be difficult to place tight analytic bounds on circuit performance \cite{Beale2018}. Contrast this against random, or \emph{stochastic}, errors, which often result from high-frequency noise in the controls or the environment. Systems with stochastic errors can usually be accurately modeled by defining a rate of various discrete errors in the system, such as a bit flips or phase flips. These errors are significantly easier to simulate on a classical computer, and their impact on quantum circuits is much easier to estimate \cite{Beale2018}.

@@

Recent works by Campbell \cite{Campbell2017,1811.08017} and Hastings \cite{Hastings2017} have shown that coherent noise can be strongly suppressed by probabilistically mixing several distinct implementations of the target quantum gates. They focus on errors arising from various gate compilations, such as the Solovey-Kitaev algorithm, for which any lingering approximation errors are generally coherent, even if the native gates are perfect. Different approximate gate compilations of the same target unitary will almost certainly result in a different unitary error. So by selecting from these compilations at random, the resulting quantum channel becomes a mixture of unitaries \note{cite Debbie Leung}, which has significiantly less coherent error than any single compilation on its own. A simple example of this reduction in coherent error by mixed quantum gates is illustrated in Fig.~\ref{fig:simple_example}. We note that randomized protocols such as theirs have a long history of outperforming their deterministic counterparts. \note{Find some citations - Viola and others - and write a sentence about them, maybe move this to the conclusion? We should also discuss randomized compiling there. }

In this article, we extend the work of Campbell and Hastings to numerically optimized quantum gates, and show that the advantages of this approach can be made robust to drift in the gate implementations. We demonstrate that, depending on the objective, different numerical optimization targets may be preferred. We present an experimental implementation of single-qubit mixed unitary controls on a superconducting qubit testbed at Rigetti Computing. Using randomized benchmarking, we are able to show a marked improvement in error rates, as well as a reduced variance in circuit outcome probabilities, indicating a reduction in the coherence of the error \cite{Ball2016}. We further provide an optimal control approach to the mixed unitary control design problem, and apply our methods in simulation where we construct single- and two-qubit mixed unitary controls which are robust to drift and uncertainty in the control parameters.  The resulting convex optimizations can be performed quickly and efficiently. \note{This paragraph is pretty good, but should be cleaned up a bit.}

% Reducing the coherence of a the quantum gate error

% 
%

% It has long been recognized, however, that one may inject additional decorrelating randomness

% By injecting additional decorrelating randomness into the system,

% By introducing additional decorrelating randomness, a number of techniques are able to convert coherent  errors into stochastic errors.

% By introducing intentional additional randomness to the 
% The gate-to-gate correlations that occur in the presence of coherent noise

% \note{don't define diamond norm here}
% The diamond distance can be used to bound the total variation distance (TVD) of a quantum circuit, but it is in general sensitive at first order to repeated application of a gate with coherent errors. For long circuits, this can add up extremely quickly, and while these errors can often be identified and reconstructed using various tomographic techniques, their impact on a given quantum  difficult to predict. Additionally, despite the relative ease of modeling stochastic errors, coherent errors are often much more likely to appear in QIPs.

@@

@@

\subsection{Representing Errors in Quantum Gates}
\noindent Suppose that one wishes to apply a unitary gate, $\mathsf{G}$, on some quantum device. Implementing this operation on a real system generally involves the application of a sequence of classical control fields to some set of qubits.  But fluctuations in the environment or imperfections in these controls can cause the state of the qubits to change in a way that is different from what was intended, \emph{i.e.}, the qubits experience errors. If the device is fairly stable with time and context\cite{1810.05651}, then we can accurately model the gate action using a completely positive, trace-preserving (CPTP) map, $\mathsf{\tilde G}$. This map can always be written as $\mathsf{\tilde G} = \mathsf{E}\circ\mathsf{G}$, where $\mathsf{E} = \mathsf{\tilde G}\circ\mathsf{G}^{-1}$ is the \emph{error map}, which is itself CPTP because $\mathsf{G}$ is unitary.

CPTP maps possesses a number of useful representations, including Kraus operators\cite{1983}, Choi matrices\cite{Choi1975}, and Jamiolkowsi states\cite{yczkowski2004}. But for the purposes of this article, the \emph{process matrix} representation will be particularly convenient\cite{OBrien2004}, and we shall denote the process matrix associated with a given CPTP map $\mathsf{G}$ with the corresponding calligraphic character, $\mathcal{G}$. For a $d$-dimensional quantum state, the process matrix is a $d^2\times d^2$ matrix. A key feature of process matrices is that they are composable and act through the usual matrix multiplication on the vectorized quantum state:
\begin{align}
	\vectorize{\mathsf{\tilde G}(\rho)}
		&= \mathcal{\tilde G}\cdot\vectorize{\rho} \\
		&= \mathcal{E}\cdot\mathcal{G}\cdot\vectorize{\rho}
\end{align}
We shall work in the basis of Pauli matrices, defining $\Sigma = \left\{I, \sigma_x, \sigma_y, \sigma_z\right\}^{\otimes n}$ as the collection of all $4^n$ $n$-qubit Pauli operators (including the identity).  In this basis,
\begin{equation}
  \vectorize{\rho}_i = \tr\!\left(\rho \cdot\Sigma_i\right)/2^n,
\end{equation}
and
\begin{equation}
	(\mathcal{\tilde G})_{ij} = \tr\!\left(\mathsf{\tilde G}\left(\Sigma_j\right) \cdot\Sigma_i\right)/2^n.
\end{equation}
Process matrices written in Pauli basis are is often referred to as \emph{Pauli transfer matrices} \cite{Chow2012}.  Error maps represented this way take the particularly nice form:
\begin{equation}\label{eq:process_matrix}
\mathcal{E} =
	\left(\begin{array}{c|cccc}
		1 &  & \vec{0}^T & \\ 
		\hline & &  &  \\
		\vec{m} &  & R &  \\
		 &  &  & 
	\end{array} 	
	\right)
\end{equation}
The top row of all trace-preserving (TP) error maps is fixed to $\{1,0,0,0,\cdots\}$ and the remainder of the first column, $\vec{m}$, describes any deviations from unitality, as might arise from amplitude damping \note{[]}. If the error map is unitary, then the error is coherent, and the unital submatrix $R$ is perfectly antisymmetric, corresponding to a rotation of the generalized Bloch vector. Importantly, if $R$ is diagonal, then the error is Pauli stochastic, with each diagonal entry corresponding to the probability that its associated Pauli error occurs in each application of the gate. If $R$ is symmetric but not diagonal, then the channel is stochastic, but the random errors consist of \emph{correlated} Pauli operators (such as $X+Y$). For a single qubit, this rounds out the possibilities, but the situation can be slightly more complicated for more qubits.

In what follows it will be useful to define the \emph{error generator}, $\mathcal{L}$, associated with a faulty gate: 
\begin{align}
	\label{eq:generator}
	\mathcal{E} 
		&= \exp\left(\mathcal{L}\right) \\
		&= \mathcal{I}_d + \mathcal{L} + \frac{1}{2}\mathcal{L}^2 + \order{\mathcal{L}^3}.
\end{align}
If an implemented gate is relatively close to the target, then the error generator will be small under any of the usual matrix norms, and the Taylor expansion above may reliably be truncated at first or second order.

\subsection{Mixed Quantum Gates}
\noindent Now suppose that we have access to an ensemble of different implementations of the target gate $\{\mathsf{\tilde G}_i\}$.
% , each associated with a different process matrix, $\mathcal{\tilde G}_i = \mathcal{E}_i\circ \mathcal{G}$. 
Each time the gate is to be applied to the system, we randomly select an implementation from this ensemble such that the probability of drawing $\mathsf{E}_i$ is $w_i$ (and we ensure that $\sum_i w_i=1$). This procedure is operationally indistinguishable from always applying the effective operation, 
\begin{align}
	\mathsf{\tilde G}_{\rm eff} &= \sum_i w_i \mathsf{\tilde G}_i.
\end{align}
We call such randomized quantum operations \emph{mixed quantum gates} or MQGs. Error metrics for MQGs can be computed in terms of their effective error map, 
\begin{equation}
	\label{eq:effective_error}
	\mathsf{E}_{\rm eff} = \sum_i w_i \mathsf{E}_i.
\end{equation}
Two important error metrics are the average gate infidelity (AGI), $\epsilon_\mathcal{F}$, and the diamond distance to the target, $\epsilon_\diamond$ \cite{}, defined as:
\begin{align}
	\label{eq:def_agi}
	&\epsilon_\mathcal{F}(\mathsf{E}) = \frac{d^2 - \tr{\mathcal{E}}}{d^2 + d},\\
	\label{eq:def_diamond}
	&\epsilon_\diamond \left(\mathsf{E}\right)
		= \frac{1}{2} \sup_\rho \vert \vert (\mathsf{I}_d\otimes \mathsf{I}_d)(\rho) 
										  - (\mathsf{E} \otimes \mathsf{I}_d)(\rho) \vert\vert_1,
\end{align}
where $d=2^n$ and $\mathsf{I}_d$ is the $d$-dimensional identity operator.  In Eq.~\eqref{eq:def_agi}, we have written the AGI for an error map, $\mathsf{E}$ in terms of its associated Pauli transfer matrix, $\mathcal{E}$. If the error channel is purely stochastic, then $\epsilon_\diamond(\error) = \epsilon_\mathcal{F}(\error)$, but if the error channel has a unitary component, then the diamond distance will generically be larger than the average gate infidelity \note{[Wallman - Error rates in quantum circuits]}. The diamond distance is subaddative \note{[Watroos TQI book]} under gate composition, so is particularly useful for constructing bounds on quantum circuit performance: the total variation distance between the outcome probabilities of a faulty and perfect quantum circuit is less than or equal to the sum of the diamond distances for the component gates \note{[Aharanov, Kitaev, Nisan, 1998]}.

Because $\epsilon_{\mathcal{F}}$ is linear in the error map, we have:
\begin{equation}
	\epsilon_{\mathcal{F}}\!\left(\mathsf{E}_{\rm eff}\right) = \sum_i w_i \,\epsilon_{\mathcal{F}}(\mathsf{E}_i).
\end{equation}
That is, the AGI of the mixed quantum gate is simply the weighted average of the component AGIs, so there is no hope of reducing the AGI by combining various implementations. However, the diamond distance is a nonlinear function of error map. As we show in the appendix (\ref{sub:diamond_distance_inequality}):
\begin{equation}
	\label{eq:diamond_ineq}
	\epsilon_\diamond\!\left(\mathsf{E}_{\rm eff}\right) \le \sum_i w_i \, \epsilon_\diamond(\mathsf{E}_i).
\end{equation}
So by mixing various implementations, each with a different error channel, the resulting channel can have a diamond distance error less than any of the component implementations.

Campbell \cite{Campbell2017} and Hastings \cite{1612.01011} independently considered this problem using gates constructed with the Solovey-Kitaev algorithm, for which many approximate gate compilations are possible. Campbell showed that, if the error generators of some ensemble of gate compilations form a convex set containing the origin, then one can construct a mixed quantum gate with quadratically suppressed diamond distance to the target. Explicitly, the weight are chosen such that the error generator is canceled to first order. Using Eqs.~\eqref{eq:effective_error} and \eqref{eq:generator}, the effective error map for a mixed quantum gate in terms of the component error generators is:
\begin{align}
	\label{eq:generators_and_effective_error}
	\mathcal{E}_{\rm eff} \simeq \left(\mathcal{I}_d + \sum_i w_i \mathcal{L}_i + \frac{1}{2} \sum_i w_i \mathcal{L}_i^2\right)
\end{align}
If, as Campbell required, the origin is in the convex hull of the generators (see Fig.~\ref{fig:vectorspace}), then there exists a choice for the weights, $w_i^*$, such that $\sum_i w^*=1$ and:
\begin{align}
	\label{eq:cancel}
	&\sum_i w_i^* \mathcal{L} = 0
	% \mathrm{with}\;&\sum_i w_i = 1
\end{align}
If the error rates of the component gates are bounded by $\alpha$, then Campbell shows that this first-order cancellation of the error generators can ensure that the error rate of the MQG is bounded by $\alpha^2$. Campbell considered error channels that were strictly unitary, so the error generators in Eq.~\ref{eq:cancel} were Hamiltonians. Hamiltonian generators can have positive or negative coefficients, so it is possible that the origin may lie in their convex hull. If, however, the error map contains stochastic components, then the condition of Eq.~\ref{eq:cancel} might be impossible to satisfy. Such errors always have positive probabilities, so the origin can \emph{never} lie in their convex hull. This can be rectified by restricting the sum in Eq.~\eqref{eq:cancel} to only the Hamiltonian component of the generators. In the rest of this paper, we will be considering gates that have only unitary errors, so we will neglect this complication going forward.

While Campbell's approach can provide a guaranteed suppression of the error rate, it does not necessarily lead to a purely stochastic channel. Second- and higher-order terms in \eqref{eq:generators_and_effective_error} can easily contribute to lingering coherent errors that impact the efficient simulability of the channel. In order to definitively eliminate these coherent errors, we seek weights, $w_i$, that annihilate the off-diagonal entries of the unital submatrix of the effective error map, resulting in an effective error:
% \begin{equation}
% 	\mathcal{E}_{eff} = 
% 	\left(\begin{array}{@{}ccccc@{}}
% 		\cdot & \cdot & \cdot & \cdot \\ 
%   		\cline{1-1}\cline{3-4}
%     	\multicolumn{1}{|c}{0} & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c}{0} & \multicolumn{1}{c|}{0} \\
%     	\cline{2-2}\cline{3-3}		
% 		\multicolumn{1}{|c}{0} & 0 & \multicolumn{1}{|c}{\cdot} & \multicolumn{1}{|c|}{0}\\
% 		\cline{3-3}\cline{4-4}	
% 		\multicolumn{1}{|c}{0} & 0 & 0 & \multicolumn{1}{|c}{\cdot}\\
% 		\cline{1-3}
% 	\end{array} 	
% 	\right).
% \end{equation}

\begin{equation}
	\mathcal{E}_{\rm{eff}} = 
	\left(\begin{array}{@{}ccccc@{}}
		1 & 0 & 0 & 0 \\ 
    	0 &  p_x & 0 & 0 \\
		0 & 0 &  p_y & 0\\
		0 & 0 & 0 &  p_z\\
	\end{array} 	
	\right).
\end{equation}
The resulting mixed quantum gate is then guaranteed to have a Pauli stochastic error channel, and significantly increasing its simulability. We can formulate this problem in analogously to the generator approach. The off-diagonal elements of the error map form a vector space, so to ensure that such a solution is possible, we need only check that the origin is in the convex hull of the vectors of off-diagonal elements for each of the component operations, $\mathcal{E}_i$.

In the remainder of this paper, we will formalize this process, presenting explicit convex optimizations to both generate a family of unitary controls and construct the optimal weighting vector. We will discuss how one might include additional desiderata, including a reduced sensitivity to environmental fluctuation as well as limiting the number of native unitaries that participate in the mixed gate.
